%-------------------------
% Resume in Latex
% Author : Manindra Gautam
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\href{#2}{#2}} \\[5pt]
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\myItem}[1]{
  \item\small{
    {#1} \\[-0.1pt]
  }
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://mkgautam.xyz}{\Large Manindra Kumar Gautam}} & Email : \href{mailto:manindragautamofficial@gmail.com}{manindragautamofficial@gmail.com}\\
  \href{https://mkgautam.xyz}{https://mkgautam.xyz} & Mobile : +91 8896813285 \\
\end{tabular*}

\vspace{20pt}
\textbf{}{I am a software engineer based in India, having 5+ years of total experience, worked on multiple projects, primarily using ReactJS and Ruby on Rails Technologies.} \\[1pt]

\resumeSubHeadingListStart
  \item{
        \textbf{Skills}{: ReactJS, TypeScript, Webpack, Ruby on Rails} \\[1pt]
  }
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tebillion Systems Pvt Ltd}{Mumbai, India}
      {Sr. Software Engineer}{May 2021 - Present}
      \resumeItemListStart
        \resumeItem{WYSDOM DENTAL PMS}
          {CloudPlus is a hardware tool that gives ability to dental practices to run it online or offline, it helps to manage and maintain practitioners and patients records. It consists of multiple micro-frontend applications.}\\[2pt]
          \textbf{Technologies: }Ruby inspired Crystal, ReactJS inspired SolidJS, Webpack Module Federation, PostgreSQL etc.
      \resumeItemListEnd

    \resumeSubheading
      {Ardentia Technologies Pvt Ltd}{Mumbai, India}
      {Sr. Software Engineer}{Apr 2019 - May 2021}
      \resumeItemListStart
        \resumeItem{WYSDOM STORE}
          {Consumable supplies to compliment Digital  X-Ray brands and many other everyday products for dentists}\\[2pt]
          \textbf{Technologies: }Ruby inspired Crystal, ReactJS, PostgreSQL etc.
        \resumeItem{WYSDOM ROTAANGEL}
          {ROTAANGEL manages shift rotas and staff holidays at busy dental practices to ease the day-to-day  admin’ load}\\[2pt]
          \textbf{Technologies: }Ruby inspired Crystal, ReactJS, PostgreSQL etc.
      \resumeItemListEnd

    \resumeSubheading
      {Akaruilabs India Pvt Ltd}{Lucknow, India}
      {Software Engineer}{Apr 2017 - Apr 2019}
      \resumeItemListStart
        \resumeItem{EQUITY MULTIPLE}
          {Equity Multiple is a US based marketplace for private real estate transactions. It enables individual and institutional investors to invest alongside the market’s most sophisticated sponsors in many commercial real estate assets.}\\[2pt]
          \textbf{Technologies: }Ruby on Rails, ReactJS, ReduxJS, Heroku, PostgreSQL etc.
        \resumeItem{ZEEHAUS}
          {Zeehaus is a US based real estate equity sharing marketplace and ownership management platform. It connects homeowners and homebuyers with investors who are enabled to purchase fractional ownership in US real estate digitally.}\\[2pt]
          \textbf{Technologies: }Ruby on Rails, ReactJS, ReduxJS, Heroku, PostgreSQL etc.
      \resumeItemListEnd

    \resumeSubheading
      {GenX Web Hosting Pvt Ltd}{Lucknow, India}
      {PHP Developer}{Dec 2015 - Jan 2017}
      \resumeItemListStart
        \resumeItem{}
          {Managed maintenance of wordpress sites, templates}\\[2pt]
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Uttar Pradesh Technical University}{Lucknow, India}
      {Bachelor of Technology in Electrical and Electronics Engineering}{Aug. 2011 -- July. 2014}
    \resumeSubheading
      {Govt Polytechnic Kanpur}{Kanpur, India}
      {Diploma in Electrical Engineering}{Aug. 2007 -- July. 2010}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Interests}
  \resumeSubHeadingListStart
    \myItem {Travelling}
    \myItem {Watching web series, movies}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
